Assignment 2

### 2019-06-29 ex2/report/report.tex
Move figures

\subsection{Interpretation}
\subsubsection{PDPs}
We generated PD plots for all features contained in our extracted feature vector. Fig.~\ref{fig:pdp} shows examples for some features for the different folds. Comparing plots generated for our deep learning and for our random forest approach, respectively, the two machine learning approaches show the outstanding difference that deep learning PDPs are smooth, while random forest PDPs fluctuate heavily. Considering the functioning of neural networks and decision trees, this is an expected result.

@@

\subsubsection{ALE plots}
In addition to PD plots, we generated ALE plots for all features in our feature vectors. Fig.~\ref{fig:ale} depicts plots for the same features as presented in Fig.~\ref{fig:pdp}.

\subsubsection{ICE plots}
Finally, we also generated ICE plots for the features. Examples are depicted in Fig.~\ref{fig:ice}. Since the dataset we used consists of 2.3 million flows, it is impossible to draw plots for all points. Fig.~\ref{fig:ice} therefore depicts a random sample of 100 flows.

@@

@@

>>>>

\subsection{Interpretation}
\subsubsection{PDPs}

We generated PD plots for all features contained in our extracted feature vector. Fig.~\ref{fig:pdp} shows examples for some features for the different folds. Comparing plots generated for our deep learning and for our random forest approach, respectively, the two machine learning approaches show the outstanding difference that deep learning PDPs are smooth, while random forest PDPs fluctuate heavily. Considering the functioning of neural networks and decision trees, this is an expected result.

@@

\subsubsection{ALE plots}

@@

In addition to PD plots, we generated ALE plots for all features in our feature vectors. Fig.~\ref{fig:ale} depicts plots for the same features as presented in Fig.~\ref{fig:pdp}.

\subsubsection{ICE plots}

@@

Finally, we also generated ICE plots for the features. Examples are depicted in Fig.~\ref{fig:ice}. Since the dataset we used consists of 2.3 million flows, it is impossible to draw plots for all points. Fig.~\ref{fig:ice} therefore depicts a random sample of 100 flows.
